Lensing

### 2014-12-13 Papers/ms.tex
A bit of writing

% Packages:
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{dsfont}

\usepackage{caption}
\usepackage{subcaption} % subfigures
\usepackage{float}

@@

\author[Brewer, Huijser and Lewis]{%
  Brendon~J.~Brewer$^{1}$\thanks{bj.brewer@auckland.ac.nz},
  David Huijser$^{1}$,
  Geraint F. Lewis$^2$
  \medskip\\
  $^1$Department of Statistics, The University of Auckland, Private Bag 92019, Auckland 1142, New Zealand\\
  $^2$Sydney Institute for Astronomy}

@@

\begin{abstract}
Gravitational lensing is a powerful astrophysical tool for studying
the distribution of matter in galaxies.
\end{abstract}

@@

\section{Introduction}

@@

\section{Source and Lens Models}
Many different approaches have been applied to gravitational lens modelling.
Any such method will involve many choices, such as:
\begin{itemize}
\item Whether to use a simply parameterized (e.g. Sersic)
or flexible (e.g. pixellated)
model for the surface brightness profile of the source
\item Whether to use a simply parameterized or flexible
model for the mass profile of the lens
\item How to compute the results (e.g. optimization methods, Markov Chain
Monte Carlo)
\end{itemize}

All such choices involve tradeoffs between convenience and realism.

@@

>>>>

% Packages:
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage{subcaption} % subfigures
\usepackage{float}

@@

\author[Brewer, Huijser and Lewis]{%
  Brendon~J.~Brewer$^{1}$\thanks{bj.brewer@auckland.ac.nz},
  David Huijser$^{1}$,
  Geraint F. Lewis$^2$
  \medskip\\
  $^1$Department of Statistics, The University of Auckland, Private Bag 92019, Auckland 1142, New Zealand\\
  $^2$Sydney Institute for Astronomy, School of Physics, A28,
  The University of Sydney, NSW 2006, Australia}

@@

\begin{abstract}
\end{abstract}

@@

\section{Introduction}
Strong gravitational lensing is a powerful astrophysical tool for studying
the distribution of matter, including dark matter, in galaxies
\citep{treu}.

@@

\section{Source and Lens Models}
Many different approaches have been proposed and applied to gravitational lens
modelling. These approaches 
\begin{itemize}
\item Whether to use a simply parameterized (e.g. Sérsic)
or flexible (e.g. pixellated) model for the surface brightness profile of the source
\item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid)
or flexible model (e.g. pixellated) for the mass profile of the lens
\item How to compute the results (e.g. optimization methods, Markov Chain
Monte Carlo)
\end{itemize}

All such choices involve tradeoffs between convenience and realism.
In a previous paper \citep{2011MNRAS.412.2521B} we argued that an ideal
modelling approach lies somewhere between simply-parameterised and
pixellated models. Simply parameterized models, such as Sérsic surface
brightness profiles for the source, and SIE models for the lens, are convenient,
they are clearly simplifications, and can produce misleading results if the
simple profiles are not a good approximation to the actual situation. On the
other hand, pixellated models for the source \citep[e.g.][]{suyu} or the lens
\citep[e.g.][]{2014MNRAS.445.2181C} can in principle represent ``any''
source surface brightness profile or lens density profile. However, the prior
distribution over pixel values is often chosen for mathematical convenience
\citep{2003ApJ...590..673W} and can assign virtually zero prior probability
to the hypothesis that the source actually looks like a galaxy.

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay,
\& Cs{\'a}nyi}{2011}]{dnest} Brewer B.~J., P{\'a}rtay L.~B., Cs{\'a}nyi G., 2011,
Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380

\bibitem[\protect\citeauthoryear{Brewer et al.}{2011}]{2011MNRAS.412.2521B} 
Brewer B.~J., Lewis G.~F., Belokurov V., Irwin M.~J., Bridges T.~J., Evans 
N.~W., 2011, MNRAS, 412, 2521

\bibitem[\protect\citeauthoryear{Brewer}{2014}]{rjobject} Brewer, B. J., 2014,
Bayesian Analysis, submitted. ArXiv: 1411.3921

\bibitem[\protect\citeauthoryear{Coles, Read, 
\& Saha}{2014}]{2014MNRAS.445.2181C} Coles J.~P., Read J.~I., Saha P., 2014, MNRAS, 445, 2181

\bibitem[\protect\citeauthoryear{O'Hagan and Forster}{2004}]{ohagan}
O'Hagan, A., Forster,~J., 2004, Bayesian inference. London: Arnold.

\bibitem[\protect\citeauthoryear{Sivia \& Skilling}{2006}]{sivia} Sivia, 
D.~ S., Skilling, J., 2006, Data Analysis: A Bayesian Tutorial, 2nd 
Edition, Oxford University Press

\bibitem[\protect\citeauthoryear{Skilling}{2006}]{skilling} Skilling, 
J., 2006, ``Nested Sampling for General Bayesian Computation'', Bayesian 
Analysis 4, pp. 833-860

\bibitem[\protect\citeauthoryear{Suyu et al.}{2006}]{suyu} 
Suyu S.~H., Marshall P.~J., Hobson M.~P., Blandford R.~D., 2006, MNRAS, 
371, 983

\bibitem[\protect\citeauthoryear{Treu}{2010}]{treu} Treu T., 2010, ARA\&A, 48, 87

\bibitem[\protect\citeauthoryear{Warren 
\& Dye}{2003}]{2003ApJ...590..673W} Warren S.~J., Dye S., 2003, ApJ, 590, 673
\end{thebibliography}
